Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-05-03 code/analysis-code/Statistical_Analysis.qmd
final2

```{r calibration-plot, fig.width=6, fig.height=6, warning=FALSE}
# 1) Plot without default legend
plot(cal,
     lty    = c(3, 1, 2),                             # dashed, solid, dashed
     col    = c("#1f78b4", "#33a02c", "#e31a1c"),     # blue, green, red
     lwd    = 2,
     xlab   = "Predicted Probability of Adverse Outcome",
     ylab   = "Observed Proportion of Adverse Outcome",
     main   = "Calibration of Gravidity Model\nin Women Aged < 25",
     legend = FALSE,                                  # <-- turn off built‐in legend
     xlim   = c(0.4, 0.8),
     ylim   = c(0.4, 0.8)
)

# 2) Add a single, custom legend
legend("bottomright",
       legend = c("Apparent", "Bias–Corrected", "Ideal"),
       col    = c("#1f78b4", "#33a02c", "#e31a1c"),
       lty    = c(3, 1, 2),
       lwd    = 2,
       bty    = "n"
)

>>>>

```{r calibration-plot, fig.width=6, fig.height=6, warning=FALSE}
library(rms)

# pick only the model variables
md <- train_data[, c("gravidity", "age_at_enrollment_years", "total_malaria_episodes", "adverse_birth_outcome")]

dd <- datadist(md)
options(datadist = "dd")

# fit the logistic model
f <- lrm(adverse_birth_outcome ~ gravidity, data = md, x = TRUE, y = TRUE)

cal <- calibrate(f, method="boot", B = 200)
# then plot(cal, ...)
